### 2016-03-16 paper.tex
Add skeletal LaTeX source

\documentclass[a4]{article}                                     
\usepackage{url,xspace,epsfig,etoolbox}
\usepackage{natbib}
\usepackage{fullpage}
\usepackage[font=bf]{caption}
\usepackage{mdwlist}

% No page numbers
\pagestyle{empty}

% Use 'Arial' font
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

% Allow point-size specification of font
\usepackage{fix-cm}

% Allow setting margins on the abstract
\usepackage{changepage}

\newcommand{\projecttitle}{Definition and directions of narrative-rich games}

% Prevent indentation of new paragraphs
\setlength{\parindent}{0pt}

% Put space after each paragraph. Note that this matches section titles too,
% and the workaround is below.
\setlength{\parskip}{\baselineskip}

% Allow easy overriding of section and subsection commands
\usepackage{titlesec}
\titleformat{\section}{\bfseries\fontsize{12}{14.4}\selectfont}{}{0em}{}
\titleformat{\subsection}{\bfseries\fontsize{11}{13.2}\selectfont}{}{0em}{}

% No blank line after section titles.
\titlespacing{\section}{0pt}{0pt}{-\baselineskip}
\titlespacing{\subsection}{0pt}{0pt}{-\baselineskip}

% No blank spaces between references
\setlength{\bibsep}{0pt}

% Hanging indent of 0.5 inches in references
\setlength{\bibhang}{0.5in}

% Keep all the screenshot figures the same width
\newcommand{\screenshotwidth}{2.5in}

% Is this blind or not?
\newtoggle{blind}
\toggletrue{blind}

\begin{document}

% Title is bold, centered, 14pt.
% Standard baseline skip is 1.2*fontsize, or 16.8 here.
\begin{center}
\fontsize{14}{16.8}\selectfont
\bf \projecttitle
\end{center}

% Gleaning author placement information from the existing proceedings.
\vspace{-0.25in}
\begin{center}
\iftoggle{blind}{
 % Nothing here: skip authors for blind review
}{
Paul Gestwicki, others, Ball State University\\
pvgestwicki@bsu.edu\\
}
\end{center}

% Abstract: 150 words or less, extra 0.5in left and right margin.
% Note that all text is justified.
%
\begin{adjustwidth}{0.5in}{0.5in}
  \textbf{Abstract:}
 Text goes here.
\end{adjustwidth}

\section{Introduction}

Content goes here

\bibliographystyle{apalike}
\bibliography{references}

\end{document}

### 2016-03-16 deploy.sh
Configure CI build to gh-pages

@@ -1,0 +1,10 @@
+#!/bin/bash
+mkdir out
+cd out
+cp ../paper.pdf .
+git init
+git config user.name "Travis-CI"
+git config user.email "travis@travis-ci.org"
+git add .
+git commit -m "Deploy to Github Pages"
+git push --force --quiet "https://${GH_TOKEN}@${GH_REF}" master:gh-pages > /dev/null 2>&1

### 2016-03-17 deploy.sh
Exit on nonzero

@@ -1,4 +1,8 @@
 #!/bin/bash
+
+# Exit with nonzero status if anything fails
+set -e
+
 mkdir out
 cd out
 cp ../paper.pdf .

### 2016-03-17 paper.tex
Add bibtex citation example
Add a ~100 word abstract draft

@@
-\documentclass[a4]{article}                                     
+\documentclass[a4paper]{article}                                     
 \usepackage{url,xspace,epsfig,etoolbox}
@@
 \begin{adjustwidth}{0.5in}{0.5in}
-  \textbf{Abstract:}
- Text goes here.
+  \textbf{Abstract:} \textit{Player-narration games} are a promising
+  genre for transformative games. This genre can be defined formal and
+  dramatic characteristics, and we identify tabletop games that belong
+  to the genre.  Adding technological components to the game affords
+  new interaction modes as well as convenient digital distribution. We
+  describe our team's pilot project at creating a technology-enhanced
+  player-narration game to improve cultural empathy among players aged
+  10--14.  This pilot project highlights several complications with
+  this genre, including thematic, technical, and production
+  challenges.  However, the pilot project justifies continued
+  experimentation, development, and formal assessment within the
+  genre.
 \end{adjustwidth}
@@
 
-Content goes here
+Content goes here.
+We might cite \citet{Koster2013}, but this example is really just a placeholder
+so the bibtex portion of the build script succeeds.
+
+\section{Acknowledgments}
+\textit{The team, organizational, and community partner
+  acknowledgments are hidden for blind review.}
 

### 2016-03-17 paper.tex
Add introduction and genre definition
There are a few holes that need to be plugged in with values from TotAN, but that's going to be more easily done from the studio with the game on hand.

@@
 
+\newcommand{\totan}{\textit{TotAN}}
+\newcommand{\smersh}{\textit{SMERSH}}
+
 % Abstract: 150 words or less, extra 0.5in left and right margin.
@@
 
-Content goes here.
-We might cite \citet{Koster2013}, but this example is really just a placeholder
-so the bibtex portion of the build script succeeds.
+\textit{Tales of the Arabian Nights}~\citep{Goldberg2009} is a 
+tabletop board game based on the eponymous folk tale.
+It was originally published in 1985~\citep{Goldberg1985} but is more commonly
+known for its 2009 re-release. 
+It is popular within the designer board game hobby with a board game
+rank of 239 (thematic rank 75) on Board Game Geek as of this writing,
+and Shut Up \& Sit Down rank it as the ninth best game of all 
+time~\citep{ShutUp2015}.
+In this game, players control a character within a mythical Arabian
+setting, and players explore the known world to accumulate Story and
+Destiny points. The winner is the one who is able to meet their 
+Story and Destiny point goal while having a successful encounter
+in Baghdad---the City of Peace.
+
+An intriguing property of \textit{Tales of the Arabian Nights}~(hereafter, \textit{TotAN}) is that it eschews the conventional wisdom for game design,
+that player immersion is related to agency.
+When a player has an encounter in \totan, they are told the name of the
+encounter---such as ``angry merchant,''  ``powerful prince,'' or
+``\textbf{put location example here}''---and based only on this information,
+they must choose a reaction from one of the given tables; for example, \textbf{put the content of one table here}.
+Another player then reads a corresponding entry from 
+the \textit{Book of Tales}, which is a \textbf{N}-page
+tome containing \textbf{N} numbered entries.
+Most entries provide introductory text followed by paragraphs
+tagged with skills that the active player may choose to use---without
+knowing the consequences. The reader then narrates the conclusion of the
+encounter and informs the player of their rewards, often in terms of
+Story or Destiny points, gaining new skills, finding treasures, or
+gaining status cards that modify players' options in future encounters.
+To summarize, the player chooses a location on the map, but they do not 
+choose what is encountered; they choose a reaction to the encounter name
+without knowing how it will be interpreted in the story;
+if they have the corresponding skill, they may choose to use it but
+without knowing whether it will help or hinder them.
+\totan{} is not a game of skill, where the player with the best tactics
+wins the game: it is somewhat arbitrary and imbalanced, but from its
+design emerges a fanciful gameplay experience. It is not played to win
+but rather to enjoy the emerging story with friends.
+
+This property of \totan{} reflects several characteristics
+of its source material,
+as our team discovered from reading youth-friendly translations suggested in the
+rulebook (specifically \citet{Neil1994}).
+Like the original stories, \totan{} is a collection of shorter stories
+that are sometimes linked together and sometimes not.
+The characters in the folk tales are often victims of fate with
+very little agency over their own encounters. The games rules follow
+cultural norms expressed in the folk tales:
+you cannot win while sex-changed or on pilgrimage, and both marriage
+and children are great blessings---unless you have an ugly baby,
+which is shameful.
+Baghdad is the most important city in the world, where your adventure starts
+and ends.
+Furthermore, many stories in \totan{} come directly from the tales,
+such as the Sindbad's escape from the valley of diamonds or Aladdin's
+being trapped in a magic cave.
+
+Playing \totan{}  inspired members of our team to read translations
+of the original tales, which made us recognize the cleverness of the design
+and its elegant dovetailing with the source material.
+Furthermore, in reading the texts, we recognized that we had already
+learned elements of the stories and the culture through playing the game,
+although not always consciously or explicitly.
+This inspired the following analysis, in which we tease apart the
+various elements of \totan{}, considering them from both game design
+and learning design points of view, and then share the results of a pilot
+project to create a technology-enhanced game within the same genre.
+
+\section{Defining the genre of player-narration games}
+
+We propose that \totan{} is one of very few games comprising a genre
+of \textit{player-narration games}, and we define this genre as having
+the following characteristics.
+
+\begin{enumerate}
+\item \textit{Take place in a believable, consistent setting.} 
+ Although the world of \totan{} may be unfamiliar to the player,
+ everything in it is representative of the world described in the original
+ folk tale---complete with the contradictions that add depth and nuance.
+
+\item \textit{Use narrative as a primary feedback mechanism.} 
+ In \totan{}, the player's reaction and skill choice yields two forms
+ of feedback: the narrative description followed by the changes to the
+ game state. The narrative is primary, both chronologically and aesthetically.
+ Note that we follow \citet{Koster2012} in treating narrative as a 
+ feedback mechanism, not a game mechanism.
+
+\item \textit{Have measurable goals.} There is a winning condition as part
+ of the social contract of play, following colloquially-accepted 
+ standards for board games. The ``game'' is not simply constrained
+ cooperative storytelling or a role-playing experience without formal end
+ conditions.
+
+\item \textit{Incorporate endogenously meaningful ambiguous decisions.}
+ Following \citet{Burgun2012}, the decisions that one makes in the game
+ are meaningful even though they are made without complete knowledge
+ of the game state. For example, a player makes 
+ the choice of reaction in \totan{} in hopes that it leads toward skills
+ that they have, such as choosing ``Fight'' while in possession of the
+ ``Weapon Use'' skill, even though one does not know whether or not
+ this skill will have relevance in the resulting entry from the
+ \textit{Book of Tales}.
+
+\item \textit{Reward players for decision-making that reflects
+    cultural understanding.}  The knowledge that a player brings to
+  bear on decisions is not just knowledge of in-game systems.  If one
+  chooses to Fight an Angry Ifrit in \totan{} without the Weapon Use
+  skill, it is probably not going to end well. This prediction is not
+  based on my having memorized the \textit{Book of Tales}, nor knowing how many
+  hit dice an Ifrit has (as in \textit{Dungeons \& Dragons} powergaming).
+  Rather, this prediction draws upon a cultural understanding of anger,
+  spirits, violence, and likely much more.
+  However, the game does this without establishing
+  ``right'' and ``wrong'' (``moral/immoral'',
+  ``light side/dark side'', ``paragon/renegade'') choices.  There
+  remain unexpected twists: perhaps fighting the Angry Ifrit without
+  combat skills makes him respect you and grant a boon.  \totan{},
+  after all, is a game that allows the player to choose to ``drink'' a
+  violent storm or ``enter'' a mysterious artifact.  While the world
+  remains consistent, it also embraces the potential for surprising
+  results.
+
+\end{enumerate}
+
+Two formal elements from \totan{} are intentionally not included in the
+genre definition above. Perhaps the most clear omission is players' reading
+each others' stories. While we agree that this is a critical element of 
+\totan{}---and that it dovetails performatively 
+and practomimetically~\citep{Travis2011} with Scheherazade's
+performances in the source material---it is not clear that this is
+characteristic to the genre.  Anecdotal evidence shows that
+players with low reading skills can ruin the play experience for other
+players, while those players could have read their own stories, aloud or not.
+Similarly, \totan{} permits a single-player experience which, while
+having a different aesthetic, still seems to produce the same general outcomes
+we described above.
+
+The other formal element omitted from the genre definition is the use of an
+explicit map. The map is an important tangible aspect of \totan{}, 
+in particular with its representation of Baghdad as the largest, most
+important city in the world. However, we also note that virtual spaces
+can be represented without such an explicit map, such as in the MUD family
+of games or choose-your-own-adventure books, both of which
+use discrete spaces without giving them visual manifestation.
+
+Analyzing \textit{Agents of SMERSH}~\citep{Maxwell2012} establishes that
+these characteristics form a genre and not merely selected elements from one
+game.
+\smersh{} is a cooperative game set in the Cold War, with players as 
+covert agents trying to stop the enigmatic Dr.\ Lobo. 
+Players move across the world collecting resources and battling henchmen,
+facing encounters clearly inspired by \totan{}: flip a card to read an
+encounter title, choose a reaction from a table, hear an introduction,
+and then get different results based on skills. Unlike \totan{},
+\smersh{} uses dice for story resolution, and supporting resource
+management mechanisms introduce important strategic decisions.
+Despite the use of dice for story resolution, the feedback is still
+primarily narrative.
+
+For contrast, consider \textit{Above and Below}~\citep{Laukat2015}, a
+worker-management game about building a city both above and below the
+surface.  \textit{Above and Below} is primarily about building an
+economic engine that generates victory points faster than your
+opponents within a fixed number of rounds. Exploring the underground
+is one source of points, and this is done by determining a random
+entry within its encounter book.  A player reads this entry aloud,
+after which the player is presented with a decision of how to
+react. However, the reaction titles are a thin wrapper around a
+risk-and-reward balance: each has a number which is the number of
+successes required on dice rolls, so players choose the highest number
+they believe they can roll. Higher numbers always equate to better results,
+and this roll is usually the end of the encounter: a successful player
+is given an in-game reward with no other story or narrative.
+Hence, although \textit{Above and Below} includes an encounter book
+that players read to each other, it does not satisfy the characteristics
+to be in the player-narration game genre.
 

### 2016-03-17 paper.tex
Stub the other sections

@@
 
+\section{Cultural Empathy and Monsters}
+
+\textit{Kay will write something here that justifies the idea of using this kind of game to teach cultural empathy, using Monsters as a hook}
+
+\section{Design Experiment}
+
+\textit{Paco will describe the team that undertook the design challenge, including the articulation of our three goals and the design elements being used to realize them}
+
+\section{Pilot Study}
+
+\textit{In which we describe what playtesting has revealed to us}
+
+\section{Conclusions and Future Work}
+
+\textit{In which we make and justify some conclusions, and point toward
+ other areas that this work could be extended}
+
 \section{Acknowledgments}

### 2016-03-18 paper.tex
Replace placeholders with real data from TotAN

@@
 encounter---such as ``angry merchant,''  ``powerful prince,'' or
-``\textbf{put location example here}''---and based only on this information,
-they must choose a reaction from one of the given tables; for example, \textbf{put the content of one table here}.
+``elephant's graveyard''---and based only on this information,
+they must choose a reaction from one of the given tables; for example, 
+table $A$ contains options to grovel, aid, rob, avoid, converse,
+attack, court, abduct, or honor.
 Another player then reads a corresponding entry from 
-the \textit{Book of Tales}, which is a \textbf{N}-page
-tome containing \textbf{N} numbered entries.
+the \textit{Book of Tales}, which is a~300-page
+tome containing~2600 numbered entries.
 Most entries provide introductory text followed by paragraphs

### 2016-03-18 paper.tex
Add quotation from Makdisi and Nussbaum
There are also some other minor typographic updates.

@@
 When a player has an encounter in \totan, they are told the name of the
-encounter---such as ``angry merchant,''  ``powerful prince,'' or
-``elephant's graveyard''---and based only on this information,
+encounter---such as angry merchant,  powerful prince, or
+elephant's graveyard---and based only on this information,
 they must choose a reaction from one of the given tables; for example, 
-table $A$ contains options to grovel, aid, rob, avoid, converse,
+table~$A$ contains options to grovel, aid, rob, avoid, converse,
 attack, court, abduct, or honor.
@@
 This property of \totan{} reflects several characteristics
-of its source material,
-as our team discovered from reading youth-friendly translations suggested in the
-rulebook (specifically \citet{Neil1994}).
+of its source material---a book that ``changed the world on a scale
+unrivalled by any other literary text''~\citep[p.1]{Makdisi2008}.
+Our team focused on the translation by \citep{Neil1994}, a youth-friendly
+version recommended in the \totan{} rulebook.
 Like the original stories, \totan{} is a collection of shorter stories

### 2016-03-22 paper.tex
Add conservative conclusions section text

@@
 
+Based on our design experiments, pilot study, and understanding of the
+literature, we believe there is a significant potential for
+culture-narration games as learning tools, particularly for
+cultural empathy.
+However, as with any educational intervention, these games do not
+come without complications.
+
+Physical games such as \totan{} and \smersh{} are expensive to produce
+and, for many, intimidating to encounter. \totan{}'s \textbf{X}-page
+instruction booklet may not faze a board game enthusiast, but we have
+observed that others are intimidated by the large rulebook, heavy box,
+and many components included in the game. Combined with the duration
+of play and complexity of rules, such games seem inappropriate for use
+in almost all formal educational settings such as conventional
+schools.  However, we have found that the combination of technology
+enhancement, grade-level writing, and shorter duration circumvents
+these problems.  Digital implementations all but eliminate
+distribution costs, and with clever game design, children can play the
+game in the relatively chaotic environment of an informal after-school
+program. With curriculum aides and improved scaffolding, such as
+post-game debriefing, we are certain the game could be easily
+integrated into school environments, particularly those with
+ready access to computers.
+
+The role of text within the game is worthy of particular attention.
+The textual expression of narrative requires that players already possess
+literacy skills: players who struggle with vocabulary or decoding words
+are easily frustrated by such games. There is an opportunity
+here as well, to differentiate text based on player reading level
+or provide embedded reading aids; however, this also transforms
+the outcome of the game from cultural empathy to reading literacy.
+Player oration---having players read aloud to each
+other---additionally requires oratory skills. We observed engagement
+being enhanced when the reader employs theatrical talents as well.
+The precise role of oratory skill, self-confidence, and the social
+contract of gameplay (the ``magic circle'') is an area for future work.
+
 \section{Acknowledgments}

### 2016-03-22 paper.tex
Add introduction paragraph about narratology and ludology

@@
 
+The role and meaning of narrative in games is a perennial topic
+of discussion among game design theorists.
+We hope to position this work not as one of ludology or narratology,
+but more pragmatically as part of a systematic investigation of how
+systems and stories interact to produce learning outcomes.
+
 \section{Defining the genre of player-narration games}
@@
 
-\textit{In which we make and justify some conclusions, and point toward
- other areas that this work could be extended}
-
 Based on our design experiments, pilot study, and understanding of the

### 2016-03-22 paper.tex
Insert Kay's prose on cultural empathy and literacy
There are also some extra additions to the references file, for future use.

@@
 
-\section{Cultural Empathy and Monsters}
+\section{Cultural Empathy}
 
-\textit{Kay will write something here that justifies the idea of using this kind of game to teach cultural empathy, using Monsters as a hook}
+We have discussed how \totan{} uses cultural understanding, not only on a
+small scale as a way to reward players, but also as a key takeaway of
+the game. In order for the game to reward players for their cultural
+understanding, we have to present cultures in a way that they can, to
+some extent, be understood. In other words, our game needs to foster a
+sense of \textit{cultural empathy}, defining ``empathy'' as 
+the ``state of mind in which someone shares the feelings or outlook of
+another, sometimes prompted by imaginative exercises 'stepping into
+someone's shoes'''~\citep[p.242]{Honderich2005}
+Therefore, cultural
+empathy, loosely formed, is having empathy for others who are from
+different cultures, which allows for better understanding of that
+culture.
+
+This goal of cultural empathy differs from a goal of \textit{cultural
+literacy} which prepares individuals to participate in another culture
+based on the information of the culture that they have been 
+given~\citep[p.165]{Hirsch1983}. Being culturally literate is having the
+ability to be able to participate in another culture that you are
+``dropped into,'' similar to how being literate is having the ability to
+understand or write a given work of text.  \totan{} focuses on a certain
+level of literacy of the given culture. Players are rewarded for their
+cultural understanding and their ability to ``perform'' in the given
+culture because of the information they have. This is demonstrated in
+the example above, understanding the cultural views of marriage and
+sex-change have an important role in game play. However, cultural
+empathy makes the main point the understanding, not the
+performance. \totan{} relies on an understanding of cultural values as
+opposed to just focusing on some of their values consequential
+norms. Therefore, though \totan{} expects some sense of cultural
+literacy, it focuses more on cultural empathy. When a player walks
+away from the game they would not have gained the ability to
+participate in either a Middle Eastern or South Asian culture;
+however, they will have gained an understanding of that culture. 
+%This
+%is why our emphasis in creating the game has relied more on cultural
+%empathy than cultural literacy. We focus more on a mindset of a
+%culture, than about facts about the culture. 
+In the context of the
+game, cultural empathy is a means to the end of cultural
+literacy. However, outside of the game, focusing on cultural literacy
+within a semi-fictional world works as the means for cultivating
+cultural empathy, particularly world culture empathy.
 

### 2016-03-22 paper.tex
Add context section

@@
 
+\section{Context}
+
+Investigating the potential for player-narration games to teach
+cultural empathy brought our team into a partnership with
+\textit{a local library branch hidden for blind review}. This branch
+serves primarily patrons from low socio-economic status, although
+its special technology education programs also draw homeschoolers from
+around the region.
+The youth patrons of the library tend to be 4rd--6th grade 
+``latchkey kids'' who 
+see the library as a place to visit with friends, to participate in programs,
+and to access technology.
+
+Conversations with program coordinators about player-narration games
+revealed that despite other differences, the youth patrons shared
+a fascination with monsters, horror, and the macabre. 
+This is in part because of cultural taboo: the youth will brag about
+being able to see a PG-13-rated movie or play an M-rated game,
+for example, and several kids worked together to produce an original
+short movie based on battles between movie monsters.
+
+The fascination exhibited by the youth patrons reflects various theses
+of Cohen's monster theory~\citep{Cohen1996}. 
+We see in their behavior that ``the same creatures who terrify and
+interdict can evoke potent escapist fantasies''~(p.16).
+Recognizing the youth patrons' attraction to this theme,
+Cohen's theory establishing monsters as reflections of culture,
+and the narrative potential of monsters,
+our team decided to engage in a design experiment to validate our
+hypotheses about player-narration games,
+in collaboration with \textit{the library branch}.
+
 \section{Design Experiment}

### 2016-03-22 paper.tex
Adopt 'culture-narration' as new genre title

@@
 
-\newcommand{\projecttitle}{Definition and directions of narrative-rich games}
+\newcommand{\projecttitle}{Definition and directions of cultural-narrative games}
 
@@
 \begin{adjustwidth}{0.5in}{0.5in}
-  \textbf{Abstract:} \textit{Player-narration games} are a promising
+  \textbf{Abstract:} \textit{Culture-narration games} are a promising
   genre for transformative games. This genre can be defined formal and
@@
   describe our team's pilot project at creating a technology-enhanced
-  player-narration game to improve cultural empathy among players aged
+  culture-narration game to improve cultural empathy among players aged
   10--14.  This pilot project highlights several complications with
@@
 
-\section{Defining the genre of player-narration games}
+\section{Defining the genre of culture-narration games}
 
 We propose that \totan{} is one of very few games comprising a genre
-of \textit{player-narration games}, and we define this genre as having
+of \textit{culture-narration games}, and we define this genre as having
 the following characteristics.
@@
 that players read to each other, it does not satisfy the characteristics
-to be in the player-narration game genre.
+to be in the culture-narration game genre.
 
@@
 
-Investigating the potential for player-narration games to teach
+Investigating the potential for culture-narration games to teach
 cultural empathy brought our team into a partnership with
@@
 
-Conversations with program coordinators about player-narration games
+Conversations with program coordinators about culture-narration games
 revealed that despite other differences, the youth patrons shared
@@
 our team decided to engage in a design experiment to validate our
-hypotheses about player-narration games,
+hypotheses about culture-narration games,
 in collaboration with \textit{the library branch}.

### 2016-03-22 paper.tex
Add information about the design experiment.

@@
 
-\textit{Paco will describe the team that undertook the design challenge, including the articulation of our three goals and the design elements being used to realize them}
+Our experiment involved a team of eleven undergraduate students and one mentor.
+The students who participated came from a variety of disciplines, including
+programming, writing, social research, and art.  The project included 
+a lot of unique tasks, so each person also contributed with their own unique 
+skills.  Each student who participated registered under three credit hours.  
+For two hours every Monday, Wednesday, and Friday, the team met to
+discuss the project and work on development together.
+
+At the beginning of the semester, the team started discussing their goals for
+the semester.  Before creating any game concepts, we discussed what our goals
+should be for the project and ended up with three:
+
+\begin{enumerate}
+
+\item \textit{A technology component.}  During our first discussions,
+we mentioned having designs that had both digital and physical components, or
+even designs that were purely physical (such as \totan).
+We decided that it was important to us that whatever we develop contain at least
+some digital component.  As we hashed out the concept of game we wanted to
+create, it ended up being completely digital.
+
+\item \textit{Cultural empathy.} Beyond adhering to the principles of culture-
+narration games, we wanted to create something that taught children
+about other cultures and why it's important to value other cultures.
+Originally, we described this as \textit{cultural literacy}, but quickly
+realized as we continued researching for our game that this already had some
+meaning that wasn't exactly what we were looking for.
+
+\item \textit{Narrative as the driving force.} Culture-narration games tell
+stories, and it was important to us that our game tell stories.  Doing this in
+a way that was interesting and processable for children proved to be one of the 
+biggest challenges.
+
+\end{enumerate}
+
+After these goals were defined, the team figured out a game concept, and 
+developed it throughout three iterations.
+The deadlines for each iteration provided the team a chance to reflect on both
+the project itself and on our methodology.  Each iteration was tested at
+\textit{the library branch}, providing valuable data for which directions we
+should bring the project.  We also had reflective meetings in which we 
+discussed what worked about our methodology, and what should change.  During
+the first two iterations, we organized our tasks using \textit{story mapping}.
+However, we realized during our second reflective meeting that it might be
+better to switch to Scrum.
+
+We used JavaFX for rough prototyping, which some of the developers had used
+before, and then moved to \textit{PlayN}, a cross-platform library that allowed
+us to build both for Java and HTML.
+Our writers and artist continually developed and improved assets for the game,
+learning how to bring them into the game easily.  The writers also developed a
+methodology for workshopping each other to make sure the narrative was 
+developed and had a consistent voice.
+
+Most of the team played vital roles in both the research side of the game and
+the development side of the game.  The writers, for example, did extensive
+research on different cultures and monsters as well as writing in a way that
+would be easy for kids to read.  Writers and developers were involved in the
+playtesting as well, and gained valuable insight on what the kids needed and
+wanted.
+
+We also invited guests to join us during our regular meeting times to talk about
+their experiences with games, monsters, and children's literacy.  One of our
+guests gave us valuable insight on what monsters mean to people and how they are
+influenced by culture.
 
